---
title: "Example - Suitability, Habitat and Resistance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Connect2)
```

# Focus Area: Ville De Nicolet

In this example, we use the pre-processed data from the Ville de Nicolet project to estimate the 
landscape suitability, habitat patches and resistance for different species.

The pre-processed datasets needed includes: \n

* ~10 spatial multiplier layers 
* LULC layer

*Note: A large part of the scripts were adapted/developed by Apex RMS and Kyle Martins

## Load the example datasets
```{r, eval=TRUE, class.source = 'fold-hide'}
data("spatialMultipliers") #Spatial multipliers estimated for Nicolet
data("landuse.r") #VNICO lulc layer

names(spatialMultipliers)

landuse.r

```

## Set the species of interest
For a full list of species and species codes, load package data using -- data(SpeciesHabSuitLookup)
and table 13 (name = species)

```{r, eval=TRUE, class.source = 'fold-hide'}
#Define the species codes
spp=c("BLBR", "MAAM", "PLCI", "RASY", "CALA")

```

## Run the Suitability function 
The function takes in the landuse layer, species and spatialMultipliers \n

An optional parameter landuseLayer defines the reference landuse layer. Default value 
for this parameter is "melcc_13"

```{r, eval=TRUE, class.source = 'fold-hide'}
#Calculate the landscape suitability index
suitability=calcSuitability(landuse.r, spp, spatialMultipliers)

suitability
```
